linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-06-07 code/linguistic_analysis_C-D.Rmd
ttr

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

@@

@@

```{r cars}
library("stringr")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(magrittr)
library(qdap)
library("stringr")
```

@@

ttr <- function(text_){
  text_ <- gsub('[[:punct:] ]+',' ',text_) ####plus remove caps
  ttr_<- type_token_ratio(text__, n.words=10)
  return(ttr_)
}

d_flowers_text <- d_flowers %>%
    group_by(gameId, blockNum, trialNum, repNum, playerId) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    select(-c(text)) %>%
    distinct()

text_block <- d_flowers_text$text_block

#d_flowers_ttr <- text_block %>%
#  mutate(ttr_v=ttr(text_block))

@@

```{r cars}
